---
title: "R Notebook"
output: html_notebook
---

# Setup
```{r}
library("tidyr")
library('ggplot2')
library('dplyr')
library("glue")

wkdir = "~/Desktop/GitHub/Obesity/NewExtractions/H9N2/timo_0.01"
setwd(wkdir)
savedir = "~/Desktop/GitHub/Obesity/NewExtractions/H9N2/timo_0.01/Output_Figures"

source("~/Desktop/GitHub/Obesity/NewExtractions/H9N2/FD_functions.R")
```

# Specifying thresholds and plotting variables
```{r}
cov_cut = 200
freq_cut = 0.01
pvalcut  = 0.05

ntlist = c("A","C","G","T")
SEGMENTS = c('H9N2_PB2','H9N2_PB1','H9N2_PA','H9N2_HA','H9N2_NP','H9N2_NA','H9N2_MP','H9N2_NS')
```

```{r}
diet = c("Obese","Lean","Control")
dietColors = c("#FF9933","#66CCFF","#606060")
names(dietColors) = diet
DietcolScale_fill <- scale_fill_manual(name = "grp",values = dietColors)
DietcolScale <- scale_colour_manual(name = "grp",values = dietColors)
```

#Loading metadata
This includes titer and Ct values when applicable. ND indicates qPCR was run with a negative result; 0 indicates plaque assay or HAI was run with a negative result. NA for any values indicate that data was missing. Sacrificed indicates there was no data at that time point because the ferret had already been sacrificed for pathology. 
```{r}
metafile = "~/Desktop/GitHub/Obesity/NewExtractions/H9N2/H9_Metadata.csv"

meta = read.csv(file=metafile,header=T,sep=",",na.strings = c(''))
meta = filter(meta, resequenced == "yes")

meta$Ct_Mgene = as.numeric(meta$Ct_Mgene)
# These NAs correspond to samples where there is no data, not samples with negative M gene results
# only non-resequenced samples have NA Ct values where that means that they were negative for the M gene
meta = filter(meta, !(is.na(Ct_Mgene)))

meta$titer = as.numeric(meta$titer)
meta$log10_titer = as.numeric(meta$log10_titer)

meta$inf_route = factor(meta$inf_route, levels = c("Index","Contact","Aerosol","Control"))
```

# Ct & Titer values for individual ferrets
```{r}
meta$inf_route = factor(meta$inf_route, levels = c("Index","Contact","Aerosol","Control"))

CT_plot = ggplot(filter(meta, inf_route == "Index" | inf_route == "Contact"), 
       aes(x = DPI, y = Ct_Mgene, color = as.character(ferretID))) +
  geom_point(size = 3) +
  geom_line(aes(group = ferretID), size = 1.5) +
  geom_hline(yintercept = 30, linetype = "dotted") +
  facet_grid(diet~inf_route) +
  PlotTheme1
print(CT_plot)
ggsave("CT_plot.png",CT_plot, path = savedir, width = 15, height = 7)

Titers_plot = ggplot(filter(meta, inf_route == "Index" | inf_route == "Contact"), 
       aes(x = DPI, y = log10_titer, color = as.character(ferretID))) +
  geom_point(size = 3) +
  geom_line(aes(group = ferretID), size = 1.5) +
  ylim(0,7) +
  facet_grid(diet~inf_route) +
  PlotTheme1
print(Titers_plot)
ggsave("Titers_plot.png",Titers_plot, path = savedir, width = 15, height = 7)
```

# Loading coverage file & segment size information
```{r}
cov = read.csv("./avg_coverage/H9N2.coverage.csv", header = TRUE, sep = ",")

seg_sizes = "~/Desktop/GitHub/Obesity/NewExtractions/H9N2/SegmentSize.csv"
sizes = read.csv(file=seg_sizes,header=T,sep=",",na.strings = c(''))
GenomeSize = (sizes %>% filter(segment == 'H9N2_GENOME'))$SegmentSize

cov$segment = factor(cov$segment, levels = SEGMENTS)
```

# Checking if data passes thresholds & make coverage plots
```{r}
cov_check = CoverageAcross(cov,cov_cut,40,sizes, wkdir)
```

```{r}
cov_qual = select(cov_check, name, quality)
cov_avgtiter = merge(cov, cov_qual, by = c("name"))

cov_avgtiter$totalcount[is.na(cov_avgtiter$totalcount)] = 0
cov_avgt = group_by(cov_avgtiter,segment,ntpos,quality) %>%
  mutate(avg_cov = mean(totalcount)) %>%
  mutate(log10_avg = log10(avg_cov))

avg_titer_plot = ggplot(filter(cov_avgt, quality == "good"), aes(x = ntpos, y = log10_avg)) +
  geom_line() +
  geom_hline(yintercept = log10(200), linetype = "dashed", color = "red") +
  facet_grid(~segment) +
  ylim(0,4.5) +
  PlotTheme1
print(avg_titer_plot)
ggsave("avg_titer_plot.pdf",avg_titer_plot,path = savedir, width = 20, height = 5)
```

Merging coverage check info with the rest of the metadata
```{r}
meta = merge(meta, cov_check, by.x = c("sample"), by.y = c("name"), all.y = TRUE) %>% unique()

nrow(meta)
count(meta,quality)
```

# Making titer plots
```{r}
# don't have titer information for W17 cohort (probably were never measured)
# don't have this info past day 6 for some ferrets sacrificed for pathology at St Jude's

m1 = filter(meta, resequenced == "yes") %>%
  #filter(quality == "good") %>% # unhashing this will plot only samples with coverage across all samples (only samples with high quality virus) 
  filter(titer != "NA" & titer != "sacrificed") %>%
  #filter(DPI == "d02" | DPI == "d04" | DPI == "d06" | DPI == "d08" | DPI == "d10" | DPI == "d12") %>%
  filter(segment == "H9N2_PB2") %>% # all segments have the same value (it's a per sample measurement), just picked first one
  group_by(inf_route, diet, DPI) %>%
  mutate(avg_titer = mean(titer)) %>%
  mutate(avg_log_titer = mean(log10_titer)) %>%
  mutate(sd_log_titer = sd(log10_titer)) %>%
  ungroup()

avg_titer = ggplot(filter(m1,inf_route == "Index" | inf_route == "Contact"), 
              aes(x = DPI, color = diet)) +
  geom_point(size = 5, aes(y = avg_log_titer)) +
  geom_jitter(size = 3, alpha = 0.4, aes(y = log10_titer)) +
  #geom_errorbar(aes(ymin = avg_log_titer - sd_log_titer, ymax = avg_log_titer + sd_log_titer)) +
  geom_line(aes(y = avg_log_titer, group = diet), linewidth = 2) +
  facet_grid(~inf_route) +
  ylim(0,6) + 
  ylab("Log10 Titer per sample") +
  PlotTheme1 +
  DietcolScale
print(avg_titer)
ggsave("avg_titer.pdf", avg_titer, path = savedir, width = 10, height = 5)
```
# Test for significance
```{r}
o_t = filter(m1,inf_route == "Contact" & diet == "Obese" & DPI == "d10") 
# All 8 segments have the same info, just picked first segment
l_t = filter(m1,inf_route == "Contact" & diet == "Lean" & DPI == "d10") 
# All 8 segments have the same info, just picked first segment

t.test(o_t$titer,l_t$titer)
# Significant comparisons at p < 0.05 with only good quality samples: Index - d08, Contact - none
# USE THIS ONE - Significant comparisons at p < 0.05 with good and bad quality samples: Index - none, Contact - none
```

```{r}
t_vals = filter(m1,inf_route == "Index" & segment == "H9N2_PB2")
aov.t_vals = aov(titer ~ diet, t_vals)
summary(aov.t_vals)
# neither index nor contact are significantly different with only good quality samples or with good + bad samples
```

# Ct Values
```{r}
ggplot(filter(m1, DPI == "d02" | DPI == "d04" | DPI == "d06" |
                DPI == "d08" | DPI == "d10" | DPI == "d12"),
       aes(x = DPI, y = Ct_Mgene)) +
  geom_point()

ggplot(filter(m1, DPI == "d02" | DPI == "d04" | DPI == "d06" |
                DPI == "d08" | DPI == "d10" | DPI == "d12"),
       aes(x = log10_titer, y = Ct_Mgene)) +
  geom_point() +
  xlim(0,8) +
  PlotTheme1

ggplot(filter(m1, log10_titer > 1), aes(x = log10_titer, y = Ct_Mgene)) +
  geom_point() +
  xlim(0,8) +
  PlotTheme1

ggplot(meta, aes(x = quality, y = Ct_Mgene)) +
  geom_point()

Ct_dist_plot = ggplot(meta, aes(x = Ct_Mgene, fill = quality)) +
  geom_histogram(binwidth = 1) +
  geom_vline(xintercept = 32, linetype = "dashed") +
  PlotTheme1 +
  ylab("Number of samples")
print(Ct_dist_plot)
ggsave("Ct_dist_plot.pdf",Ct_dist_plot,path = savedir, width = 7, height = 5)
```

```{r}
m2 = filter(meta, resequenced == "yes") %>%
  filter(quality == "good") %>% 
  # if we're only interested in active infections/sequenced virus, then we should only consider samples where all segments have good coverage
  # but including bad quality shows the trend of fewer samples at later time points better
  filter(segment == "H9N2_PB2") %>%
  group_by(inf_route, diet, DPI) %>%
  mutate(avg_ct = mean(Ct_Mgene)) %>%
  mutate(sd_ct = sd(Ct_Mgene)) %>%
  ungroup()

avg_ct_plot = ggplot(filter(m2,inf_route == "Index" | inf_route == "Contact"), 
              aes(x = DPI, color = diet)) +
  geom_point(size = 5, aes(y = avg_ct)) +
  geom_jitter(size = 3, alpha = 0.4, aes(y = Ct_Mgene, shape = quality)) +
  #geom_errorbar(aes(ymax = avg_ct + sd_ct, ymin = avg_ct - sd_ct)) +
  geom_line(aes(y = avg_ct, group = diet), linewidth = 2) +
  facet_grid(~inf_route) +
  #ylim(0,6) + 
  ylab("Ct Value") +
  PlotTheme1 + 
  scale_y_reverse() +
  DietcolScale
print(avg_ct_plot)
ggsave("avg_ct_plot.pdf", avg_ct_plot, path = savedir, width = 10, height = 5)
```

# Testing for significance
```{r}
o_ct = filter(m2,inf_route == "Contact" & diet == "Obese" & segment == "H9N2_PB2" & DPI == "d02") 
# Ct value measured for the M gene, but all 8 have the same info from merging earlier
l_ct = filter(m2,inf_route == "Contact" & diet == "Lean"& segment == "H9N2_PB2" & DPI == "d02") 
# Ct value measured for the M gene, but all 8 have the same info from merging earlier

t.test(o_ct$Ct_Mgene,l_ct$Ct_Mgene)
# USE THIS ONE - Significant comparisons at p < 0.05 with only good quality samples: Index - d04 Contact: none
# Significant comparisons at p < 0.05 with good and bad quality samples: Index - d04 Contact: none
```

```{r}
ct_vals = filter(m2,inf_route == "Index" & segment == "H9N2_PB2")
aov.ct_vals = aov(Ct_Mgene ~ diet, ct_vals)
summary(aov.ct_vals)
# neither index nor contact are significantly different with only good quality samples or with good + bad samples
```