---
title: "Analysis of FCC Samples"
output:
  html_document:
    df_print: paged
---

Load libraries
```{r}
library("tidyr")
library("plyr")
library('ggplot2')
library('dplyr')
library("glue")
library(ggVennDiagram)

wkdir = "~/Desktop/GitHub/Obesity/FCC"
setwd(wkdir)
savedir = "~/Desktop/GitHub/Obesity/FCC/Output_Figures"

source("~/Desktop/Obesity/OLD/FromKate/FD_functions.R")
```

Specifying thresholds and plotting variables
```{r}
diet = c("Obese","Lean","Control")
dietColors = c("#FF9933","#66CCFF","#606060")
names(dietColors) = diet
DietcolScale_fill <- scale_fill_manual(name = "grp",values = dietColors)
DietcolScale <- scale_colour_manual(name = "grp",values = dietColors)

cov_cut = 200
freq_cut = 0.02
pvalcut  = 0.05

ntlist = c("A","C","G","T")
SEGMENTS = c('H9N2_PB2','H9N2_PB1','H9N2_PA','H9N2_HA','H9N2_NP','H9N2_NA','H9N2_MP','H9N2_NS')
INFECTIONS = c("Index","Direct","Aerosol","Control")
```

# Pre-Sequencing Analysis

FCC alignment dataframe set up
```{r}
flu_align = read.csv("flu.alignment.csv", header = TRUE, sep = ",")

flu_align = separate(flu_align, Sample, into = c("FerretID","DPI","Rep"))
flu_align$Sample = paste0(flu_align$FerretID,"_",flu_align$DPI,"_",flu_align$Rep)
flu_align$FerretID_DPI = paste0(flu_align$FerretID,"_",flu_align$DPI)

flu_align1 = filter(flu_align, Rep == "rep1")
flu_align2 = filter(flu_align, Rep == "rep2")

flu_align = merge(flu_align1, flu_align2, by = c("FerretID","DPI","FerretID_DPI"))

flu_align$TotalReads.avg = ((flu_align$TotalReads.x + flu_align$TotalReads.y) / 2)
```

FCC alignment plot
```{r}
FCC_align = ggplot(flu_align, aes(x = FerretID_DPI, y = log10(TotalReads.avg))) +
  geom_point() + 
  ylim(0,6) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  PlotTheme1
print(FCC_align)
ggsave("FCC_align.png", FCC_align, path = savedir)
```
# Sequencing Analysis

Loading in coverage file & segment size information
```{r}
cov = read.csv("H9N2.coverage.csv", header = TRUE, sep = ",")

seg_sizes = "SegmentSize.csv"
sizes = read.csv(file=seg_sizes,header=T,sep=",",na.strings = c(''))
GenomeSize = (sizes %>% filter(segment == 'H9N2_GENOME'))$SegmentSize

cov$segment = factor(cov$segment, levels = SEGMENTS)
```

Checking if data passes thresholds & make coverage plots
```{r}
cov_check = CoverageAcross(cov,cov_cut,80,sizes, wkdir)
```

Loading in variant files & metadata
```{r}
varfile = "H9N2.VariantsOnly.0.01.200.csv"
metafile = "FCC_Metadata.csv"

# read and rearrange the data
vars = read.csv(file=varfile,header=T,sep=",",na.strings = c(''))
vars$name = vars$sample

meta = read.csv(file=metafile,header=T,sep=",",na.strings = c(''))
meta = merge(meta, cov_check, by.x = c("sample"), by.y = c("name"))

meta$titer = as.numeric(meta$titer)
meta$Ct_Mgene = as.numeric(meta$Ct_Mgene)
```

Rearranging variant dataframe
```{r}
vdf = ArrangeVarWRep(vars)
```

Filtering variant df by metadata
```{r}
vdf = merge(vdf,meta, by = c("sample","segment"))
vdf = filter(vdf, quality == "good")
vdf = vdf[!duplicated(vdf), ] %>% droplevels()

vdf$segment = factor(vdf$segment, levels = SEGMENTS)
vdf$inf_route = factor(vdf$inf_route, levels = INFECTIONS)
```

Tallying number of ferrets with variants
```{r}
fercount = select(vdf, ferretID,DPI,diet,inf_route,cohort)
fercount = fercount[!duplicated(fercount), ]  %>% 
  unique() %>% 
  group_by(DPI, diet, inf_route, cohort) %>% 
  tally()
```

Plotting ferret tally
```{r}
ggplot(fercount, aes(x = DPI, y = n, fill = diet)) +
  geom_col(position = "stack") +
  facet_grid(~inf_route) +
  ylab("Number of Ferrets with SNVs") +
  PlotTheme1 +
  DietcolScale_fill
```

Removing SNVs under frequency and coverage cutoffs
```{r}
minorvdf = filter(vdf, minorfreq >= freq_cut & totalcount >= cov_cut & minor %in% ntlist) %>% 
            droplevels()
minorvdf = minorvdf[!duplicated(minorvdf), ] %>% droplevels()

# doesn't remove any SNVs here in this case
```

Tallying SNVs
```{r}
# can make these groupings whatever you want

# count the number of SNVs per sample
group_list_seg = c('ferretID','segment',"DPI","diet","inf_route","cohort") # counts across each segment 
group_list_gen = c('ferretID',"DPI","diet","inf_route","cohort") # Counts across entire genome

seg_count = TallyIt(minorvdf, group_list_seg, "snv_count")
gen_count = TallyIt(minorvdf, group_list_gen, "snv_count") 

# Average Number of Variants per Sample
gen_count_avg = group_by(gen_count, DPI, diet, inf_route) %>%
  mutate(avgSNV = mean(snv_count), sdSNV = sd(snv_count))
```

Calculating Shannon Entropy
```{r}
minorvdf = ShannonPos(minorvdf)
minorvdf$SegmentSize = as.numeric(minorvdf$SegmentSize)
minorvdf$shannon_perkb = (minorvdf$segment_shan/(minorvdf$SegmentSize/1000))
minorvdf$normalized_shannon = (minorvdf$shannon/GenomeSize)

# shannon_ntpos = shannon entropy at that nt pos - should always be between 0 and 1 for each sample
# segment_shan = sum of all nt_pos per segment for each sample
# shannon = sum of all segment_shan across genome for each sample
# shannon_perkb = segment shannon per kb (segment specific) for ach sample
# normalized_shannon = shannon divided by genome size (can make per kb by dividing by 1000) for each sample

# Average Shannon Entropy per Site per Sample (using normalized_shannon)
shan_g = select(minorvdf, ferretID, DPI, diet, inf_route, normalized_shannon) 
shan_g = shan_g[!duplicated(shan_g),]
shan_g_avg = group_by(shan_g, DPI, diet, inf_route) %>% 
  mutate(avgShan = mean(normalized_shannon), sdShan = sd(normalized_shannon))

shan_segkb = select(minorvdf, ferretID, DPI, diet, inf_route, segment, shannon_perkb)
shan_segkb = shan_segkb[!duplicated(shan_segkb),]
shan_segkb_avg = group_by(shan_segkb, DPI, diet, inf_route, segment) %>% 
  mutate(avgShan = mean(shannon_perkb), sdShan = sd(shannon_perkb))
```

Making plots for variant tallies and Shannon entropy 
```{r}
VarPlot = ggplot(gen_count_avg, aes(x=DPI, fill = diet)) +
  geom_col(aes(y = avgSNV, group = diet), position = "dodge") +
  geom_jitter(aes(group = diet, y = snv_count), width  = 0.15) +
  geom_errorbar(aes(ymin = avgSNV - sdSNV,
                    ymax = avgSNV + sdSNV)) +
  ylab("Average number of SNVs per sample") +
  facet_grid(~inf_route+diet) +
  PlotTheme1 +
  DietcolScale_fill
print(VarPlot)
ggsave(VarPlot, file = "VariantCount.pdf", path = savedir)

ShannonPlot = ggplot(shan_g_avg, aes(x=DPI, fill = diet)) +
  geom_col(aes(y = avgShan, group = diet), position = "dodge") + #plots average
  geom_jitter(aes(y = normalized_shannon, group = diet), width  = 0.15) + #plots value for each sample
  geom_errorbar(aes(ymin = avgShan - sdShan,
                    ymax = avgShan + sdShan)) +
  ylab("Average Shannon entropy per site across genome") +
  facet_grid(~inf_route+diet) +
  PlotTheme1 +
  DietcolScale_fill
print(ShannonPlot)
ggsave(ShannonPlot, file = "MeanShanPerSite.pdf", path = savedir)

ShannonPlot2 = ggplot(shan_segkb_avg, aes(x=DPI, fill = diet)) +
  geom_col(aes(y = avgShan, group = diet), position = "dodge") + # plots average
  #geom_point(aes(y = shannon_perkb, group = diet)) + # plots value for each segment, sample
  #geom_errorbar(aes(ymin = avgShan - sdShan,
  #                  ymax = avgShan + sdShan)) +
  ylab("Average Shannon entropy per kB across segments") +
  facet_grid(~segment) +
  PlotTheme1 +
  DietcolScale_fill
print(ShannonPlot2)
ggsave(ShannonPlot2, file = "MeanShanPerSegKB.pdf", path = savedir)
```

Do the number of variants correlate with titer or Ct?
```{r}
meta_small = select(meta,"ferretID","DPI","diet","inf_route","cohort", "titer","Ct_Mgene","avg_coverage")
varcount = merge(gen_count_avg, meta_small, by = c("ferretID","DPI","diet","inf_route","cohort"))

ggplot(varcount, aes(x = snv_count, y = log10(titer), color = diet)) +
  geom_point() +
  ylim(0,8) +
  PlotTheme1 +
  DietcolScale
# will get a warning when NAs are removed

ggplot(varcount, aes(x = snv_count, y = Ct_Mgene, color = diet)) +
  geom_point() +
  ylim(0,30) +
  PlotTheme1 +
  DietcolScale
# will get a warning when NAs are removed
```

SNV location plots
```{r}
SNVLocation = ggplot(minorvdf, aes(x = ntpos, y = ferretID)) +
  geom_point(aes(color = diet, shape = cohort)) +
  facet_grid(inf_route~segment) +
  PlotTheme1 +
  DietcolScale
print(SNVLocation)
ggsave(SNVLocation, file = "SNVLocation.pdf", path = savedir)

minorvdf$var = paste0(minorvdf$segment,"_",minorvdf$ntpos,minorvdf$minor)

# Comparing to SNVs found in the stock

stock = filter(minorvdf, DPI == "Stock")
stock = stock[!duplicated(stock), ]
stocksnv = levels(factor(stock$var))
length(stocksnv)

ferrets = filter(minorvdf, DPI != "Stock")
ferrets = ferrets[!duplicated(ferrets), ]

shared_w_stock = ferrets %>% filter(var %in% stocksnv)
dim(shared_w_stock)
ferunique = ferrets %>% filter(!(var %in% stocksnv))
dim(ferunique)

StockSharedPlot = ggplot(shared_w_stock, aes(x = ntpos, y = ferretID)) +
  geom_point(aes(color = diet, shape = cohort)) +
  facet_grid(inf_route~segment) +
  PlotTheme1 +
  DietcolScale +
  ggtitle("SNVs found in stock")
print(StockSharedPlot)
ggsave(StockSharedPlot, file = "StockSharedPlot.pdf", path = savedir)

FerUniquePlot = ggplot(ferunique, aes(x = ntpos, y = ferretID)) +
  geom_point(aes(color = diet, shape = cohort)) +
  facet_grid(inf_route~segment) +
  PlotTheme1 +
  DietcolScale +
  ggtitle("SNVs not found in stock")
print(FerUniquePlot)
ggsave(FerUniquePlot, file = "FerUniquePlot.pdf", path = savedir)
```

Venn diagram of obese and lean SNVs
```{r}
o_var = filter(ferrets, diet == "Obese") 
o_var = unique(o_var$var)

l_var = filter(ferrets, diet == "Lean") 
l_var = unique(l_var$var)

diet_var <- list(Obese = o_var, Lean = l_var)

DietUniqueSNVS = ggVennDiagram(diet_var)
print(DietUniqueSNVS)
ggsave(DietUniqueSNVS, file = "DietUniqueSNVS.pdf", path = savedir)
```

Obese- and lean-specific SNVs
```{r}
lean = ferrets %>% 
  filter(var %in% l_var) %>% 
  filter(!(var %in% o_var)) %>% 
  group_by(var) %>% 
  mutate(count = 1, totalsamp = sum(count))

obese = ferrets %>% 
  filter(var %in% o_var) %>% 
  filter(!(var %in% l_var)) %>% 
  group_by(var) %>% 
  mutate(count = 1, totalsamp = sum(count))

dietunique = rbind(lean,obese)
dietunique = dietunique[!duplicated(dietunique), ] %>% droplevels()
  
DietUnique = ggplot(dietunique, aes(x = ntpos, y = segment)) +
  geom_point(aes(size = totalsamp, color = nonsyn)) + 
  ggtitle("Number of samples containing each variant - diet specific") +
  theme(legend.key = element_blank(),
         strip.background = element_rect(colour="black", fill="white"),
         axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  facet_grid(~diet) +
  PlotTheme1
print(DietUnique)
ggsave(DietUnique, filename = "SegmentSNVPlot_DietUnqique.pdf", path = savedir)

shared = ferrets %>% 
  filter(var %in% o_var) %>% 
  filter(var %in% l_var) %>% 
  group_by(var) %>% 
  mutate(count = 1, totalsamp = sum(count))

SharedPlot = ggplot(shared, aes(x = ntpos, y = segment)) +
  geom_point(aes(size = totalsamp, color = nonsyn)) +
  ggtitle("Number of samples containing each variant - Shared between diet groups") +
  theme(legend.key = element_blank(),
         strip.background = element_rect(colour="black", fill="white"),
         axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  PlotTheme1
print(SharedPlot)
ggsave(SharedPlot, filename = "SegmentSNVPlot_DietShared.pdf", path = savedir)
```

```{r}
ggplot(ferrets, aes(x = minorfreq)) +
  geom_histogram(binwidth = 0.01)

highfreq = filter(ferrets, minorfreq > 0.25)
```